% This is the acknowledgments page of my

\cleartorecto % A memoir-class command for moving the acknowledgments to a recto page, not verso.
\chapter{Acknowledgements} % For the heading on the page, also registers in the table of contents
\thispagestyle{plain} %This page should have numbers.



% Elena
First and foremost, I would like to thank my advisor, Elena Aprile.  Not only have you provided support and guidance throughout my time at Columbia but you have given me countless opportunities to learn and grow over my years in the group.  You have been such an inspiration to me and have been a phenomenal mentor.  I will also never forget how you took a chance on me in helping me transfer to Columbia and having me join your group --- I can honestly say that I would not be where I am today without you.


% Luke, Marc, and Guillaume
I would also like to give a special thanks to Luke Goetzke, Marc Weber, and Guillaume Plante for all of their help and guidance during my first few years at Columbia.  You all had seemingly infinite patience and I could not have asked for better teachers and role models.


% Postdocs
I would also like to thank all of the postdoctoral fellows and research scientists who taught, challenged, and mentored me over the course of my Ph.D.  Antonio Jesus Melgarejo Fernandez, Patrick de Perio, Marcello Messina, Qing Lin, and Fei Gao, you all have been an incredible inspiration and I cannot thank you enough for all of your support.  


% Grad Students
I would also like to thank my fellow graduate students Zach Greene, Yun Zhang, Joey Howlett, and Tianyu Zhu.  I have had so much fun working with you all over the years and I have learned so much from all of you and would not have succeeded without you.  


% Marcela
I would also like to give a special thanks to Marcela Stern.  It has been such a pleasure working with you and getting to know you over the years.  You are one of the kindest and most helpful people I know and have made the last few years so enjoyable.


% Collaboration
I cannot thank my colleagues in the XENON collaboration enough for their hardwork and dedication that has made our joint effort such a success.  It has been a privilege to be part of such an extraordinary group of people.


% Physics Friends
I would also like to thank my friends Felix Clark, Zach Green, Ryne Carbone, and Russell Smith.  It has been incredible to get to know you all over the last few years and it was so helpful to always have people to talk to and hang out or grab a beer with through the trial and tribulations of graduate school.  


% Parents
I am extremely grateful for my incredible and loving parents, Elizabeth and Robert.  They not only have been supportive of me in more ways than I can name but they always instilled in me the virtues that have allowed me to get this far.  There is no way that I would be where I am today without their guidance and help and I owe you both a debt of gratitude that can never be repaid.  This achievement is as much yours as it is mine.



% Brothers and sisters, Beth and Steve, Haveners
I am also extremely thankful to my brothers and sisters: Allison, Alexandra, Halie, Kurt, Ryan, and Sara.  I would also like to thank my new parents, Georgiana and Henry, who have always been incredibly supportive throughout my studies and my New York parents, Beth and Steve.  You all mean the world to me and your encouragement over the last five years has been so critical to me being able to push through and keep moving through the tough times.  I never would have made it this far without you.


% Laura
Finally, I would like to thank my incredibly intelligent, talented, and beautiful wife, Laura.  Words cannot possibly describe how much you mean to me.  From our first summer doing research together, you have not just been an encouraging force but a source of inspiration.  You fought with me side-by-side through classes, the qualifying exams, and research and I never would have made it through without you.  I can never thank you enough for giving me the strength and confidence to get this far.  It is hard for me to think about closing this chapter together but I look forward to writing the rest of our story with you.  %It's sad to me that we're about to close this chapter of our lives but I look forward to writing the rest of our story.




